SciPy - some descriptive title here

### 2018-04-12 scipy-1.0/paper.tex
BUG: restructure doc flow (reference figure)

    Consider the following asv benchmark results, spanning roughly nine years of project history. These demonstrate the gradual performance
    improvements in a nearest-neighbor search, \texttt{scipy.spatial.cKDTree.query()} using the command:

@@

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
    \end{figure}

>>>>

    Consider the asv benchmark results shown in Figure~\ref{fig:asv-bench}, spanning roughly nine years of project history. These demonstrate the gradual performance
    improvements in a nearest-neighbor search through \texttt{scipy.spatial.cKDTree.query()}, and can be run using the command:

@@

        \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
        \label{fig:asv-bench}
    \end{figure

@@
